%-*- Mode:LaTeX; -*-      
\documentclass[11pt]{article}
\usepackage{vmargin}		% Force narrower margins
\setpapersize{USletter}
\setmarginsrb{1.0in}{1.0in}{1.0in}{0.6in}{0pt}{0pt}{0pt}{0.4in}
\setlength{\parskip}{.1in}  % removed space between paragraphs
\setlength{\parindent}{0in}

\usepackage{epsfig}
\usepackage{graphicx}

\newcommand{\ra}{$\rightarrow$}
\begin{document}

\large
\begin{center}
{\bf CS-6340, Written Assignment \#3} \\
{\bf Aishwarya Asesh (u1063384)}
\end{center}
\normalsize
{\bf Question 1}
\begin{enumerate}

\item {\bf AGENT - John} cleared {\bf THEME - the sidewalk} with his {\bf INSTRUMENT - snow shovel}. 

\item {\bf THEME - A raffle} was held for {\bf BENEFICIARY - the local charity.} 

\item {\bf AGENT - Joe} teamed up with {\bf CO-AGENT - Susan} to learn how to {\bf THEME - ski.} 

\item  {\bf RECIPIENT - Tom} was given {\bf THEME - a bike.} 

\item {\bf THEME - The dress} was purchased by {\bf AGENT - Lisa} with {\bf CO-THEME - matching shoes.} 

\item {\bf AGENT - Julie} mailed her {\bf RECIPIENT - grandmother} {\bf THEME - a letter.} 

\item {\bf EXPERIENCER - George} hopes that {\bf THEME - his car} can be fixed.

\item {\bf THEME - The image} was created with {\bf INSTRUMENT - Adobe Photoshop} by {\bf AGENT - a cartoonist.}

\newpage
{\bf Question 2}
\begin{quote}
\hspace*{.5in} $word1$ : $<$9 2 8 0$>$ \\
\hspace*{.5in} $word2$ : $<$6 7 4 5$>$  \\
\hspace*{.5in} $word3$ : $<$1 3 9 2$>$ 
\end{quote}

\begin{enumerate}


\item Similarity($word1$, $word2$) using Manhattan Distance.  \\ 

We know Manhattan Distance = $(\vec {X}, \vec {Y})$ = $\sum ^{N}_{i=1} |x_{i} - y_{i} |$\\
Thus here Manhattan Distance = $|(9-6)| + |(2-7)| + |(8-4)| + |(0-5)|$\\
= 3 + 5 + 4 + 5\\
= 17\\


\item Similarity($word2$, $word3$) using Manhattan Distance.  \\ 

We know Manhattan Distance = $(\vec {X}, \vec {Y})$ = $\sum ^{N}_{i=1} |x_{i} - y_{i} |$\\
Thus here Manhattan Distance = $|(6-1)| + |(7-3)| + |(4-9)| + |(5-2)|$\\
= 5 + 4 + 5 + 3\\
= 17\\


\item Similarity($word1$, $word2$) using Jaccard Similarity.  \\

We know Jaccard $(\vec {X}, \vec {Y})$ = $\frac { \sum^{N}_{i=1} \min (x_{i},y_{i})} { \sum^{N}_{i=1} \max (x_{i},y_{i})}$\\
Thus here Jaccard = 6 + 2 + 4 + 0 / 9 + 7 + 8 + 5\\
= 12 / 29\\

\item Similarity($word2$, $word3$) using Jaccard Similarity.  \\

We know Jaccard $(\vec {X}, \vec {Y})$ = $\frac { \sum^{N}_{i=1} \min (x_{i},y_{i})} { \sum^{N}_{i=1} \max (x_{i},y_{i})}$\\
Thus here Jaccard = 1 + 3 + 4 + 2 / 6 + 7 + 9 + 5\\
= 10 / 27\\

\item Similarity($word1$, $word2$) using Cosine Similarity.  \\ 

We know Cosine $(\vec {X}, \vec {Y})$ = $\frac { \sum^{N}_{i=1} (x_{i}*y_{i})} {\sqrt {\sum^{N}_{i=1} x_{i}^{2}} \sqrt {\sum^{N}_{i=1} y_{i}^{2}}}$\\
Thus here Cosine = (9*6 + 2*7 + 8*4 + 0*5) / $(\sqrt {9^{2} + 2^{2} + 8^{2} + 0^{2}} * \sqrt {6^{2} + 7^{2} + 4^{2} + 5^{2}})$\\
= (100) / (12.20)*(11.22)\\
= (100) / (136.88)\\


\item Similarity($word2$, $word3$) using Cosine Similarity.  \\ 

We know Cosine $(\vec {X}, \vec {Y})$ = $\frac { \sum^{N}_{i=1} (x_{i}*y_{i})} {\sqrt {\sum^{N}_{i=1} x_{i}^{2}} \sqrt {\sum^{N}_{i=1} y_{i}^{2}}}$\\
Thus here Cosine = (6*1 + 7*3 + 4*9 + 5*2) / $(\sqrt {6^{2} + 7^{2} + 4^{2} + 5^{2}} * \sqrt {1^{2} + 3^{2} + 9^{2} +2^{2}})$\\
= (73) / (11.22)*(9.74)\\
= (73) / (109.28)\\


\end{enumerate}


\newpage
{\bf Question 3}
\begin{center}
\begin{tabular}{|lll|} \hline
\textbf{NP}  & \textbf{CONTEXT} & \textbf{CLASS} \\ \hline
Apple tablet          & mobile computer & {\sc product} \\
British tablet        & computer tech & {\sc product} \\
Microsoft tablet      & mobile computer  & {\sc product} \\
Apple                 & tech giant  & {\sc company} \\
Apple Corporation     & tech leader  & {\sc company} \\
Microsoft             &  leader & {\sc company} \\
Microsoft Corporation & tech giant  & {\sc company} \\
British Tablet Corporation & mobile computer giant & {\sc company} \\ \hline
\end{tabular}
\end{center}

For Part A:\\
Rules generated from NP present in the table above:\\

{\bf Noun Phrase} - If contains (Apple), P (product) is 1/3, P (company) is 2/3\\  
{\bf Noun Phrase} - If contains (British), P (product) is 1/2, P (company) is 1/2\\
{\bf Noun Phrase} - If contains (Corporation), P (product) is 0/3, P (company) is 3/3\\
{\bf Noun Phrase} - If contains (Microsoft), P (product) is 1/3, P (company) is 2/3\\
{\bf Noun Phrase} - If contains (Tablet), P (product) is 3/4, P (company) is 1/4\\

For Part B:\\
Rules generated for each contexts present in the table above:\\

{\bf Context} - If contains (computer), P (product) is 3/4, P (company) is 1/4\\  
{\bf Context} - If contains (giant), P (product) is 0/3, P (company) is 3/3\\
{\bf Context} - If contains (leader), P (product) is 0/2, P (company) is 2/2\\
{\bf Context} - If contains (mobile), P (product) is 2/3, P (company) is 1/3\\
{\bf Context} - If contains (tech), P (product) is 1/4, P (company) is 3/4\\


\newpage
{\bf Question 4}\\[15pt]
{\bf S1:} Trout can be found in many Utah rivers.  \\
{\bf S2:} The Utah Symphony hired a new bass player.  \\
{\bf S3:} John Smith plays an electric bass guitar.  \\
{\bf S4:} A soprano and bass will sing with the symphony. \\
{\bf S5:} Ray Charles is learning to play the electric bass guitar. \\
{\bf S6:} The Utah aquarium displays an electric eel, bass, and guitar fish. \\
{\bf S7:} The Utah fisherman caught a river trout. \\

We know Salience (word, category) =$\frac{P (word/category)}{P (word)}$, So we will be using this for following proofs:\\

\begin{enumerate}
\item salience(Utah, {\sc fish}) \\
P (Utah/fish) = (S1) (S6) (S7) / (S1) (S6) (S7) (S2) = 3/4 \\
P (Utah) = (S1) (S6) (S7) (S2)/60 = 4/60\\
P (Utah/fish)/ P (Utah) = (3/4) / (4/60) = 45/4 \\

\item salience(electric, {\sc fish})  \\ 
P (electric/fish) = (S6) (S5) / (S1) (S5) (S6) (S7) = 2/4 \\
P (electric) = (S3) (S6) (S5)/60 = 3/60\\
P (electric/fish)/ P (electric) = (2/4) / (3/60) = 10\\


\item salience(bass, {\sc fish})  \\ 
P (bass/fish) = (S6) (S5) / (S1) (S5) (S6) (S7) = 2/4 \\
P (bass) = (S2) (S3) (S4) (S5) (S6)/60 = 5/60 \\
P (bass/fish)/ P (bass) = (2/4) / (5/60) = 6\\

\item salience(Utah, {\sc music}) \\
P (Utah/music) = (S6) (S2) / (S2) (S3) (S4) (S6) (S5) = 2/5\\
P (Utah) = (S2) (S1) (S6) (S7)/60 = 4/60 \\
P (Utah/music)/ P (Utah) = (2/5) / (4/60) = 6\\ 

 \item salience(electric, {\sc music}) \\
P (electric/music) = (S3) (S6) (S5) / (S2) (S3) (S4) (S6) (S5) = 3/5\\
P (electric) = (S3) (S6) (S5)/60 = 3/60\\
P (electric/music)/ P (electric) = (3/5) / (3/60) = 12\\


 \item salience(bass, {\sc music}) \\
P (bass/music) =(S2) (S3) (S4) (S6) (S5) / (S2) (S3) (S6) (S5) (S4) = 5/5 \\
P (bass) = (S2) (S3) (S6) (S5) (S4)/60 = 5/60\\
P (bass/music)/ P (bass) = (5/5) / (5/60) = 12\\

\end{enumerate}


\newpage
{\bf Question 5}
\begin{enumerate}
\item List all possible  noun phrase (NP) antecedents for the first instance
  of ``He'' (underlined)  that satisfy gender  agreement.  \\ 
John Smith, John

\item List all possible  noun phrase (NP) antecedents for ``them'' (underlined) that
  satisfy \\ animacy  agreement.   \\ 
INANIMATE - groceries, oranges

\item List all possible  noun phrase (NP) antecedents for ``them'' (underlined) that satisfy \\ number   agreement.  \\ 
too many groceries, 10 oranges

\item List all of the reflexive pronouns in the story.  \\ 
himself

\item List all of the possessive pronouns in the story. \\
his, his, their, her

\item List all of the pleonastic pronouns in the story.  \\ 
it

\item List all instances of appositives in the story. \\
Mary, his neighbor, \\her husband, George, who was in the next aisle
 
\end{enumerate}

\end{enumerate}  


\end{document}

